Synthesis of Rules for Network Intrusion Detectors

### 2019-10-23 paper/paper.tex
supported options table

\Fix{tabulate some important rules that we support}

>>>>

\begin{table}[h]
  \caption{\label{table:rules}Supported options}  
  \centering
  \begin{tabular}{lllll}
    \toprule
    \multicolumn{1}{c}{\#} & \multicolumn{1}{c}{Option} &  \multicolumn{1}{c}{Description}\\
    \midrule     
    1 & dsize & matches on the size of the packet payload\\
    2 & itype & matches on a specific ICMP type\\
    3 & icode & matches on a specific ICMP code\\
    4 & icmp\_seq & checks a ICMP sequence number\\
    5 & icmp\_id & matches on specific ICMP id-values\\
    6 & window & check for a specific TCP window size\\
    7 & flags & matches on TCP flags\\
    8 & fragbits & checks if the fragmentation or reserved bits are set in the IP header\\
    9 & threshold & used to control the rule’s alert frequency\\
    10 & content & matches on bytes of the payload\\
    \bottomrule
  \end{tabular}
\end{table}
